Do Alternate Wetting and Drying Irrigation Technology and Nitrogen Rates Affect Rice Sheath Blight?

### 2020-06-25 analysis/paper/paper.Rmd
Edits in the Discussion for clarity and update a references

As the rice establishment method is known to affect the spread of sheath blight [@Willocquet2000].
Manually transplanted rice had higher apparent infection rates than direct seeded rice.
As manual transplanting becomes less common due to labor and water availability constraints [@Toriyama2005], sheath blight risk may be decreased due changes in establishment practices.
A combination of AWD and direct seeded rice could be beneficial for both saving water and reducing the risk of sheath blight.

@@

Readers may find a reproducible research compendium that recreates this paper, which includes all data generated from this project and code used for analysis as a reproducible research compendium from <https://doi.org/...> [@Sparks2019].

>>>>

The rice establishment method is known to affect the spread of sheath blight [@Willocquet2000].
Manually transplanted rice has been found to have higher apparent infection rates than direct seeded rice.
Therefore, as manual transplanting becomes less common due to labor and water availability constraints [@Toriyama2005], sheath blight risk may be decreased due changes in establishment practices.
A combination of AWD and direct seeded rice could be beneficial for both saving water and reducing the risk of sheath blight.

@@

Readers may find a reproducible research compendium that recreates this paper, which includes all data generated from this project and code used for analysis as a reproducible research compendium from <https://doi.org/...> [@Sparks2020].
The data are freely and openly available from <https://doi.org/10.5281/zenodo.3889800> [@Sparks2020a].
